Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: Step 1, 2: wording

This first step might appear useless, but as of now we already have
made some choices with regard to the API of our library.  By giving a
usage example, we were forced to think about which arguments our
function takes.  We can now run Doctest to verify that the example
works.

@@

We add a specification that forces our function to actually calculate
fibonacci numbers.

@@

\noindent Of course, this test now fails when we run it,

@@

\noindent so we add a working implementation.  Both Doctest and Hspec
are happy now.

>>>>

\noindent This first step might appear useless, but as of now we
already have made some choices with regard to the API of our library.
By giving a usage example, we were forced to think about which
arguments our function takes.  We can now run Doctest to verify that
the example works.

@@

In the next step, we add a specification that forces our function to
actually calculate fibonacci numbers.

@@

\noindent Of course, this spec fails when we run it,

@@

\noindent so we add a working implementation.  Both Doctest and Hspec
report success after this.
